Analysis of split plot design using MCMCglmm

### 2017-04-28 Analysis.Rmd
Clean up Analysis.Rmd/md
Remove NTIL/NTShB in 2016 data
In some cases the number of infected tillers recorded is higher than
the number of tillers in the hill. I've recoded these two columns to be
NA where this happens

After doing this I've regenerated the data graphs for Tiller Sheath
Blight Severity Over Time and rerun the analysis for TSHB AUDPS

**_THIS IS BEING REVISED_**

This analysis is unlikely to be the correct approach. The data are being examined
again and a new analysis will be conducted that accounts for the ordinal scale
used for data collection for severity.

However, these analyses should be correct for the tiller sheath blight incidence.

@@

# R Session Info
```{r session_info}
sessionInfo()
```

>>>>

@@

# R Session Info
```{r session_info}
devtools::session_info()
```
